The Shape and Color of Politics

### 2023-10-24 chapter_2/src/slides/slides.qmd
making some more edits to job talk slides

## The study of visuals in politics

@@

## A snap-judgment model of **visual** political information processing

@@

> There obviously is a strong association with blue and the Democratic Party and red and the Republican Party. We've seen in some of our testing that specifically MAGA red tends to elicit a slightly stronger association with Republicans/conservatives/Trump than other shades. The rest of color spectrum doesn't seem to have as strong an association, though greens and purples tend to read a little more left, the combination of red, white and blue tends to read a little more right, black and white tends to read a little left, black and red tend to read a little more right, etc.

@@

@@

@@

>>>>

![[@zaller_simple_1992]](../../assets/slides/imgs/zaller_feldman.png){.absolute right=100 top=0}
![[@zaller_nature_1992]](../../assets/slides/imgs/zaller.jpg){.absolute right=100 bottom=0}
![[@lodge_rationalizing_2013]](../../assets/slides/imgs/lodge_taber.jpg){.absolute left=100 top=0}
![[@taber_illusion_2016]](../../assets/slides/imgs/taber_lodge_2016.png){.absolute left=100 bottom=0}

But what about visual information?

<!--
## The study of visuals in politics

@@

-->
## A snap-judgment model of **visual** political information processing

@@

> There obviously is a strong association with blue and the Democratic Party and red and the Republican Party. We've seen in some of our testing that specifically MAGA red tends to elicit a slightly stronger association with Republicans/conservatives/Trump than other shades.
---

@@

## How this fits in with the rest of the book?

- <span style="color: #616A6B"> How do colors convey political information and effect individual attitudes? </span>
- How do colors influence political deliberation?
- How do colors influence neighborhood evaluations?

## How my book fits in with the rest of my work?

:::: {.columns}

::: {.column width="50%"}
How identity is communicated; its effects

- Party Identification (this book)
- Gender and politics
- Racial and ethnic politics
:::

::: {.column width="50%"}
Methodological

- Text as data
- Images as data
- Data munging
- Multiple imputation
:::

::::

@@

### Full snap-judgment model

{{< include ../../../assets/_theory.qmd >}}

@@

#### List of model specifications for Study 2

- [Moderated by age](#moderated-by-age)
- [Moderated by colorblindness](#moderated-by-colorblindness)
- [Dependent on the amount of the color red and blue](#h_2a)
- [Include treatment indicator variables in the same model](#single-model)
